---
title: "Varitaion_Graphs"
output: pdf_document
date: '2022-06-21'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Loading Packages
```{r}
library(ggplot2)
library(plotly)
```

Graph Part 1:
For First Stage:
- filter by each site, then choose one specific param to filter for.
- For each Site, create box and whisker plot (Necessary to get summary stats?)

```{r plot pt. 1}
var1 <- plot_ly()
as_holder <- active_sites_param
for(s in sites){
  active_sites_param <- as_holder
  #Double filter for Site and Parameter (Pick DO as example)
  active_sites_param <- active_sites_param %>% filter(Station.Name == s) %>% 
    filter(Parameter == "Dissolved Oxygen")
  var1 <- var1 %>% add_trace(y = active_sites_param$Value, type = "box")
}
var1
```


Plot with Bass Connections Data, plot different instances of sampling as traces,
y value still value of singular parameter.

```{r File in Data and Clean it}
bc_data <- read.csv(file = "SS1-SS2_Merged.csv")
dates <- c("9/25/21", "2/26/22")
```


```{r Plotly Plot 2}
var2 <- plot_ly()
as_holder2 <- bc_data

for(d in dates){
  bc_data <- as_holder2
  bc_data <- bc_data %>% filter(DATE == d)
  var2 <- var2 %>% add_trace(y = bc_data$DO.mg.L, type = "box")
}
var2
```

Box Plots for Durham Data Over Time

Get just month and year out of the dates:
```{r}
#for(date in active_sitesReal$Date.Time){
  split_yr <- active_sitesReal
  split_yr$Date.Time <- substr(split_yr$Date.Time, 0, 4)
years <- c("2004", "2005", "2006", "2007", "2008", "2009", "2010", "2011",
           "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019", 
           "2020", "2021", "2022")
```

```{r plot}
var3 <- plot_ly()
as_holder3 <- split_yr

for(y in years){
  split_yr <- as_holder3
  split_yr <- split_yr %>% filter(Date.Time == y) %>% 
    filter(Parameter == "Dissolved Oxygen")
  
  var3 <- var3 %>% add_trace(y = split_yr$Value, type = 'box')
  print("ran")
}
split_yr <- as_holder3
var3
```

